---
title: "p8105_hw1_tw2918"
output: github_document
date: "2023-09-16"
---

# Problem 1
1. Load the moderndive library, and the early_january_weather dataset:

```{r}
library(moderndive)
```

```{r}
data("early_january_weather")
```

2. Write a short description of the dataset using inline R code

* Variables in this dataset
  * There are 15 variables in this dataset, which shows the weather in Newark from January 1st to January 15th, 2023. 
    1. `origin` variable shows the location of the data and only have one value `origin = EWR`.
    2. `year` `month` `day` and `hour`variables shows the date and time of the data. The `year` and `month` variables only have one value `year = 2013`, `month = 1`. The `day` and `hour` are categorical variables with value `day = 1-15`,`time = 0-23` .
    3. `temp` is the temperature dgrees in fahrenheit
    4. `dewp` is the dew point, showing the temperature the air needs to be cooled to (at constant pressure) in order to achieve a relative humidity (RH) of 100%.
    5. `humid` is the humidity of the air in percentage.
    6. `wind_dir` is the wind direction of the time in degrees.
    7. `wind_speed` is the wind speek of the time in meters per second.
    8. `wind_gust` is wind guest,  a brief increase in the speed of the wind, measured in miles per hour
    9. `precip`is the precipitation, showing the chance newark will be receive snow.
    10. `pressure` is the weather pressure measured in millibars.
    11. `visib` is the visiblity in kilometers.
    12. `time_hour` listed year, month, date and time. 

* Size of the dataset
  * There are 358 observations in this dataset
  * The number of row of this dataset is `r nrow(early_january_weather)`.
  * The number of columns of this dataset is `r ncol(early_january_weather)`.

* The mean temperature
  * The mean temperature is `r mean(early_january_weather$temp)`.

3. Make a scatterplot of temp (y) vs time_hour (x); color points using the humid variable. Describe patterns that are apparent in this plot.

* Make a scatterplot of temp (y) vs time_hour (x)
  *load `tidyverse` library for the plot. Otherwise, the file won't knit.
```{r}
library(tidyverse)
```

  * Use ggplot()funtion for the scatterplot, list the dataset in the parentheses followed by x and y variable in aes parentheses. Must + geom_point(), otherwise the no dot will appear in th scatterplot. 
```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp)) + geom_point()
```

  * color points using the humid variable.
```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid )) + geom_point()
```

  * Describe patterns that are apparent in this plot.
    * The temprature is incresing from January 1st to January 15th. The humidity is also increasing from January 1st to January 15th. There's temperature difference during the day.The temperature will first increase from 12am and then decrese during the day to the night. Generally speaking, it is more humid at night than during the day. 
    
  * Export your scatterplot to your project directory.
```{r}
ggsave("hw1_scatterplot_temp_timhour_humid.png")
```

# Problem 2
1. Create a data frame comprised of:
* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r}
hw1_df=
  tibble(
    num_samp = rnorm(10),
    log_vec = num_samp >0,
    cha_vec = character(10),
    fac_vec = factor(x = 10, 3)
  )
```



  